Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-11-19 paper.qmd
Added initial table for scDEED
Added 3 layouts for three UMAP hyperparameters

>>>>

#### scDEED

```{r}
result_umap <- read_rds(here::here('data/pbmc3k/pbmc_scdeed_umap_results.rds'))

result_umap |>
  kableExtra::kable(format = "latex",
                    booktabs = TRUE,
                    longtable = TRUE,
                    label = "scdeedumap") |>
  kableExtra::kable_styling(latex_options = "scale_down")
```

```{r}
#| label: read-pbmc-umap-layouts
# Read a variety of different NLDR representations of PBMC
# and plot them on same aspect ratio
umap_pbmc1 <- read_rds("data/pbmc3k/pbmc_scdeed_umap_n_neighbors_30_min_dist_0.3.rds")
umap_pbmc1 <- as_tibble(umap_pbmc1)
names(umap_pbmc1) <- c("UMAP1", "UMAP2")

nldr1c <- umap_pbmc1 |>
  ggplot(aes(x = UMAP1,
             y = UMAP2)) +
  geom_point(alpha=0.1, size=1, colour='#a65628') +
  interior_annotation("a")

umap_pbmc2 <- read_rds("data/pbmc3k/pbmc_scdeed_umap_n_neighbors_5_min_dist_0.01.rds")
umap_pbmc2 <- as_tibble(umap_pbmc2)
names(umap_pbmc2) <- c("UMAP1", "UMAP2")

nldr2c <- umap_pbmc2 |>
  ggplot(aes(x = UMAP1,
             y = UMAP2))+
  geom_point(alpha=0.1, size=1, colour='#999999') +
  interior_annotation("b")

umap_pbmc3 <- read_rds("data/pbmc3k/pbmc_scdeed_umap_n_neighbors_15_min_dist_0.99.rds")
umap_pbmc3 <- as_tibble(umap_pbmc3)
names(umap_pbmc3) <- c("UMAP1", "UMAP2")

nldr3c <- umap_pbmc3 |>
  ggplot(aes(x = UMAP1,
             y = UMAP2))+
  geom_point(alpha=0.1, size=1, colour='#f781bf') +
  interior_annotation("c")
```

```{r}
#| label: fig-pbmc-mse-umap
#| fig-pos: H
#| out-height: 100%

wrap_plots(nldr1c, nldr2c, nldr3c, ncol = 3)
```
